\begin{thebibliography}{99}

\bibitem{crispdm2000}
Chapman P., Clinton J., Kerber R., Khabaza T., Reinartz T., Shearer C., Wirth R.
\newblock \textit{CRISP-DM 1.0: Step-by-step data mining guide}.
\newblock SPSS Inc., 2000.

\bibitem{han2011}
Han J., Kamber M., Pei J.
\newblock \textit{Data Mining: Concepts and Techniques}.
\newblock 3rd ed., Morgan Kaufmann, 2011.

\bibitem{leakage2023}
Kaufman S., Rosset S., Perlich C., Stitelman O.
\newblock Leakage in data mining: Formulation, detection, and avoidance.
\newblock \textit{ACM Transactions on Knowledge Discovery from Data}, 2012.

\bibitem{mtg-jamendo}
Bogdanov D. et al.
\newblock The MTG-Jamendo dataset for automatic music tagging.
\newblock \url{https://mtg.github.io/mtg-jamendo-dataset/}, truy cập 2025.

\bibitem{librosa}
McFee B. et al.
\newblock librosa: Audio and music signal analysis in Python.
\newblock \textit{Proc. SciPy}, 2015.

\bibitem{spotify-api}
Spotify AB.
\newblock Spotify Web API Documentation.
\newblock \url{https://developer.spotify.com/documentation/web-api}, truy cập 2025.

\bibitem{deezer-api}
Deezer.
\newblock Deezer API Documentation.
\newblock \url{https://developers.deezer.com/api}, truy cập 2025.

\bibitem{gemini-embed}
Google DeepMind.
\newblock Gemini Embedding models.
\newblock \url{https://ai.google.dev/gemini-api/docs/embeddings}, truy cập 2025.

\bibitem{mer-survey}
Kim Y. E. et al.
\newblock Music emotion recognition: A survey.
\newblock \textit{Proc. ISMIR}, 2010.

\bibitem{weak-labels}
Ratner A. J. et al.
\newblock Data programming: Creating large training sets, quickly.
\newblock \textit{NeurIPS}, 2016.

\end{thebibliography}
